Vibrations and Heat Diffusion on the Unit Disc

### 2020-04-17 writeup/draft2.tex
minor edits

@@

% \begin{figure}[!htb]
%     \minipage{0.32\textwidth}
%       \includegraphics[width=\linewidth]{images/waves1.png}
%     \endminipage\hfill
%     \minipage{0.32\textwidth}
%       \includegraphics[width=\linewidth]{images/waves2.png}
%     \endminipage\hfill
%     \minipage{0.32\textwidth}%
%       \includegraphics[width=\linewidth]{images/waves3.png}
%     \endminipage
%     \caption{Solutions to the wave equation for a given initial velocity.}
%     \end{figure}

>>>>

In order to solve this equation, we again separate the variables, now assuming that $\psi(r,\phi)=f(r)g(\phi)$. If we insert this into the Helmholtz equation and divide by $\psi$ we obtain:
  \frac{1}{f(r)}\left[r^2 \dder{^2 f}{r^2} + r \dder{f}{r}+k^2 r^2\right] = -\frac{1}{g(\phi)}\dder{^2 g}{\phi^2}
Again the left-hand side is a function of $r$ only, and the right hand side is a function of $\phi$ only. The condition on the radial equation is that $f(1) = 0$. The condition on the angular equation is less obvious though. In order to get physical results, as well as to make sense of partial derivatives, we require our functions to be twice differentiable. This implies that our angular equation must at the very least be continuous, and therefore we have the implicit condition that $g(0)=g(2\pi)$.

@@
